%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{article} % Default font size
\thispagestyle{empty}

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Alexander Pisarev} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> 154 Belgrove park, Clontarf,\\ % Address line 1
\> Co. Dublin, Ireland, D03 Y0E9 \\ % Address line 2
{\bf Date of Birth} \> 9$^{th}$ March 1992 \\ % Date of birth 
{\bf Nationality} \> Russian % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +353 83 069 2755 \\ % Mobile phone
{\bf Email} \> \href{mailto:alexander.a.pisarev@gmail.com}{alexander.a.pisarev@gmail.com} \\ % Email address
{\bf Skype} \> pisarev\_a@live.com \\ % Skype username
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

C++ software developer with experience in cross-platform programming (Linux, Windows, MacOSX). Interested in studying new technologies and programming languages.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2009-2014} \> Specialist (Master's like degree) in Computational and Applied Mathematics - \\[3pt]
\>National Research Nuclear University MEPhI, Moscow, Ruusian Federation, tel.: +7 (495) 788 5699 \\[5pt]
\>Average score 4.6/5
\>\+
\textit{Final project 'Distributed computational system' (5/5)}
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{Jul 2018 -}{Present}
{Arista Networks, 2 George's Dock, IFSC, Dublin, Co. Dublin, Ireland, tel.: +1-408-547-5500}
{https://www.arista.com}
{Software Engineer, Routing Team}
{
Technology stack: C++, python, golang, gtest, clang tools.
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item{Developed features for Bgp implementation}
\item{Designed and implemented tooling and CI extension to support multiple compilers}
\item{Promoted using of c++ unit test framework and clang sanitizers}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Dec 2016 -}{Jun 2018}
{Yandex LLC, Lva Tolstogo st. 18, Moscow, Russian Federation, tel.: +7 (495) 739 7000}
{http://www.yandex.ru}
{Software Developer, Yandex Browser}
{
Technology stack: C++, clang tools, python, chromium.
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item{Refactored code and improved large scale project stability}
\item{Upstreamed changes to a Chromium project}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Mar 2015 -}{Nov 2016}
{Virtuozzo, Altufevskoe Highway 44, Moscow, Russian Federation, tel.: +7 (495) 783 2977}
{http://www.virtuozzo.com}
{Software Developer, Server virtualization}
{
Technology stack: C++, python, perl, Boost, libvirt, logstash, elasticsearch, MySQL, SQLite.
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item{Designed and implemented major features of Virtuozzo Automator}
\item{Maintained several project repositories (review code, merge changes and build packages)}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Feb 2014 -}{Feb 2015}
{Logos - Agent technologies LLC, Shipilovskaja st. 28a, Moscow, Russian Federation, tel.: +7 (495) 995 5218}
{}
{Developer}
{
Main programming language: C++. Libraries and tools: MFC, Qt. DB: MS SQL.
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item{Developed a tool to automate a 3D scene creation and a Moscow subway training simulator}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Sep 2011 -}{Jan 2014}
{ITAR-TASS, Tverskaja av. 2, Moscow, Russian Federation, tel.: +7 (499) 791 0444}
{http://www.tass.ru}
{IT Specialist}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\begin{multicols}{2}
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item Languages - C++, python, golang, perl, ruby
\item Development for Linux, Windows and MacOS
\item Databases - MS SQL, MySQL
\item Version control systems - git, svn, perforce
\item Unit-testing, refactoring, agile methodology
\item Parallel and concurrent programming
\end{itemize-noindent}
\end{multicols}

\end{document}
