%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size
\thispagestyle{empty}

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Pisarev Alexander} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> Kostjakova st. 11k1-16,\\ % Address line 1
\> Moscow, Russian Federation \\ % Address line 2
{\bf Date of Birth} \> 9$^{th}$ March 1992 \\ % Date of birth 
{\bf Nationality} \> Russian % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +7 (926) 665 7968 \\ % Mobile phone
{\bf Email} \> \href{mailto:tresrus92@gmail.com}{tresrus92@gmail.com} \\ % Email address
{\bf Skype} \> tresmephi \\ % Skype username
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

C++ software developer with experience in cross-platform programming (Linux, Windows, MacOSX). Interested in studying new technologies and programming languages.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2009-2014} \> Specialist (BC like degree) in Computational and Applied Mathematics - \\[3pt]
\>National Research Nuclear University MEPhI, Moscow \\[5pt]
\>Average mark 4.6/5
\>\+
\textit{Final project 'Distributed computational system' (5/5)}
}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{Dec 2016 -}{Present}
{Yandex LLC, Lva Tolstogo st. 18, Moscow, Russian Federation}
{http://www.yandex.ru}
{Software Developer, Yandex Browser}
{
Main programming language: C++. Project based on chromium. Script languages: python.
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item{Participated in a large scale project with multi-process architecture as a part of distributed team}
\item{Made a code refactoring and a product stability improvement}
\item{Upstream changes to a Chromium project}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Mar 2015 -}{Nov 2016}
{Virtuozzo, Altufevskoe Highway 44, Moscow, Russian Federation}
{http://www.virtuozzo.com}
{Software Developer, Server virtualization}
{
Main programming language: C++. Libraries: Boost, libvirt. Tools: logstash, elasticsearch. DB: MySQL, SQLite. Script languages: bash, perl, python.
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item{Designed and implemented major features of Virtuozzo Automator}
\item{Maintained several project repositories (review code, merge changes and build packages)}
\item{Reworked and adapted VM guest tools for new versions of OSes (X Windows support, new network management tools)}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Feb 2014 -}{Feb 2015}
{Logos - Agent technologies LLC, Shipilovskaja st. 28a, Moscow, Russian Federation}
{}
{Developer}
{
Main programming language: C++. Libraries and tools: MFC, Qt. DB: MS SQL.
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item{Developed a tool to automate a 3D scene creation}
\item{Developed a metropoliten training simulator}
\end{itemize-noindent}
}

%------------------------------------------------

\job
{Sep 2011 -}{Jan 2014}
{ITAR-TASS, Tverskaja av. 2, Moscow, Russian Federation}
{http://www.tass.ru}
{IT Specialist}
{
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item{Created a subsystem for receiving, processing and sending XML documents}
\end{itemize-noindent}
}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\begin{multicols}{2}
\begin{itemize-noindent}
\setlength\itemsep{0em}
\item Advanced in C++, STL, Boost
\item Basic knowledge of Python, Perl, Ruby
\item Linux development (Bash, Posix API)
\item Windows development (WinAPI)
\item Base knowledge of SQL DB (MS SQL, MySQL)
\item Experience with VCS (git, svn)
\item Experience in modern development methodologies (unit-tests, refactoring, agile)
\item Knowledge of networking principles and OS structure
\item Experience in parallel and concurrent programming
\item Knowledge of algorithms and data structures
\end{itemize-noindent}
\end{multicols}

\end{document}
